%========================================================
%    SCHOLARSHIPS & AWARDS (Short Style)
%========================================================
%\ressection{Scholarships & Awards}
\noindent\textbf{Scholarships + Awards}:
  \begin{itemize}
    \item \textbf{2016 Hack for the Sea}; 1st Prize (with A.J. Teti); Cape Ann, MA. \\
      Description:
      Received 1st Prize for the conceptualization and prototyping 
      of "HooknUp.Net," a fish-identification-and-social-media app
      envisioned to to help marine scientists track fish populations
      via crowd sourcing and deep-learning-based computer vision.
      Further description and details available upon request.
    \item \textbf{2012 Heliophysics Summer School (HSS): Heliophysics Exploration};  
      HSS Scholarship - NASA Living with a Star (LWS) and
      University Corporation for Atmospheric Research (UCAR); Boulder, CO.
      % https://cpaess.ucar.edu/heliophysics/summer-school
    \item \textbf{2011 Planetary Science Summer School (PSSS): Spacecraft Mission Design using Concurrent Systems Engineering}; 
      Scholarship - NASA Jet Propulsion Laboratory (JPL),  California Institute of 
      Technology (CalTech); Pasadena, CA.
      % https://www.jpl.nasa.gov/edu/intern/apply/nasa-science-mission-design-schools/
    \item \textbf{2010 Summer School on Operator Algebras and Conformal Field Theory};
      Summer Travel Grant/Scholarship - NJIT; Eugene, OR (University of Oregon).
    \item \textbf{2009 Field Work in Peru: Ground-Based LIDAR/Imagers for Lower-Atmospheric Weather Systems}; 
      Summer Travel Grant -  NJIT; Huancayo, Peru.
    \item \textbf{2008 Field Work at Jenny Jump State Forest (JJSF), NJ: Magnetometer Installation and Real-Time Geomagnetic Monitoring System}; 
      2008 Summer Research Grant -  NJIT; Newark, NJ, and JJSF, NJ.
    \end{itemizie}


%========================================================
%    SCHOLARSHIPS & AWARDS (Long Style)
%========================================================
%\lnr{Concurrent Systems Engineering for Mission Design (2011)}{Planetary Science Summer School (Scholarship), Jet Propulsion Laboratory}
%\lnr{Operator Algebras and Conformal Field Theory (2010)}{Summer School (Scholarship), U. Oregon}
%\lnr{Ground-Based LIDAR/Imagers for Lower-Atmospheric Weather Systems (2009)}{Summer Work in Peru (Research Grant), NJIT}
