%========================================================
%   INVITED PRESENTATIONS
%========================================================
\vspace{0.2cm}
\ressection{Invited Presentations}

%%%% 2015
\begin{center} \Large{2015} \end{center}
\normalsize
\begin{itemize*}
  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, and A. T. Weatherwax,
    ``Quantifying Solar Wind-Polar Cap Interactions,'' {\em American
    Geophysical Union Fall Meeting}, San Francisco, CA. Dec 14-18, 2015.

  \item K. Urban, ``Sailing the Seas of the Solar Wind,'' {\em Meeting
    of the North Jersey Astronomical Group}, Montclair State University,
    Montclair, NJ. Nov. 11, 2015.

  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, and A. T. Weatherwax,
    ``\href{http://cedarweb.vsp.ucar.edu/wiki/images/0/0c/2015-06-23_PREZ_CEDAR_SW-PC-interaction.pdf}{Solar
    Wind-Polar Cap Open Field Interactions \textsuperscript{\tiny{[link]}}},'' Coupling, Energetics, and
    Dynamics of Atmospheric Regions [CEDAR], 2015 Meeting, Seattle, WA

  \item
    Urban, K.,
    ``\href{http://www.slideshare.net/inverseuniverse/2015-0302-prezafrlagofluxgatedataquality?ref=http://www.kevin-urban.com/prez.shtml}{AGO
    Fluxgate Data: Extracting value from an imperfect time series \textsuperscript{\tiny{[link]}}},''
    Air Force Research Laboratory, Albuquerque, NM
\end{itemize*}


%%%% 2011
\begin{center} \Large{2011} \end{center}
\normalsize
\begin{itemize*}

  \item K. Sayanagi, J. Balcerski, B. Carande, R. Diaz-Silva, S. Diniega
    A. Fraeman, S. Guzewich, J. Hudson, A. Nahm, S. Potter, M. Route, K.
    Urban, S. Vasisht, B. Benneke, S. Gil, R. Livi, B. Williams,
    ``Trojan ASteroid Tour, Exploration, and Rendezvous: TASTER
    Mission,'' {\em Jet Propulsion Laboratory}, Pasadena, CA. August
    2011.
\end{itemize*}




%%%% 2008
\begin{center} \Large{2008} \end{center}
\normalsize
\begin{itemize*}
  \item
    Urban, K., and A. Gerrard, ``Geomagnetic Research at Jenny Jump: the
    Magnetic Forecast,'' {\em Meeting of the United Astronomy Clubs of
    New Jersey}, Jenny Jump State Forest, NJ. July 19, 2008.
\end{itemize*}

