%========================================================
%   REGULAR PRESENTATIONS
%========================================================

%%%% 2016
\begin{center} \Large{2016} \end{center}
\normalsize
\begin{itemize*}
  \item
    Urban, K., A. J. Gerrard, A. T. Weatherwax, L. J. Lanzerotti, J. D. Paterson, 
    ``Leveraging the Polar Cap: Ground-Based Measurements of the Solar Wind,'' 
    American Geophysical Union [AGU] Fall Meeting, 
    San Francisco, CA. December, 2016.
  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, and A. T. Weatherwax, 
    ``Rethinking Magnetic Coordinates at High Latitudes: Solar Wind Hydromagnetic Energy in the Polar Cap,'' 
    Geospace Environment Modeling [GEM] Summer Workshop, 
    Santa Fe, NM. June 21, 2016.
  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, and A. T. Weatherwax, 
    ``ULF Power in the Deep Polar Cap,'' 
    Geospace Environment Modeling [GEM] Summer Workshop,
    Santa Fe, NM. June 22, 2016.
\end{itemize*}

%%%% 2015

%%%% 2014
\begin{center} \Large{2014} \end{center}
\normalsize
\begin{itemize*}
  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, A. T. Weatherwax,
    ``\href{http://adsabs.harvard.edu/abs/2014AGUFMSA13B3992U}{Locating
    the Open-Closed Boundary During the Passage of a Corotating
    Interaction Region \textsuperscript{\tiny{[link]}}},'' American Geophysical Union [AGU]  Fall
    Meeting, San Francisco, CA. December 15-19, 2014.

  \item 
    Gerrard, A., L. Lanzerotti, J. Manweiler, J. Bortnik, and K. Urban,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:0EnyYjriUFMC}{Modulation
    of Ring Current He-Ions by Bounce-Resonant ULF Waves \textsuperscript{\tiny{[link]}}},'' 
    American Geophysical Union [AGU] Fall Meeting, San Francisco, CA.
    December 15-19, 2014.

  \item Urban, K., A. Gerrard, L. Lanzerotti, and A. Weatherwax, ``The
    Fluxgate Open-Closed Boundary,'' {\em Geospace Environment Modelling
    [GEM] ``Mini-GEM'' Workshop}, San Francisco, CA. December 14, 2014.

  \item Urban, K. D., A. J. Gerrard, A. T. Weatherwax, L. J.
    Lanzerotti, and A. Ridley, ``Observations of the open-closed
    boundary during the passage of a corotating interaction
    region,'' {\em 2014 SCAR Biennial Meeting}, Auckland, New
    Zealand. August 23 - September 3, 2014.

  \item 
  Urban, K., A. Gerrard, and L. Lanzerotti, ``Open-Closed Boundary
  Reconstruction: Cooperative Space-borne and Ground-based Methods,''
  {\em Geospace Environment Modeling [GEM] Summer Workshop},
    Portsmouth, VA. June 15-20, 2014.

  \item
    Urban, K., A. J. Gerrard, and L. J. Lanzerotti,
    ``\href{http://rbspgway.jhuapl.edu/rbsp_SWG_Mar_2014}{Ground-based ULF
    observations associated with Zebra Stripe Events \textsuperscript{\tiny{[link]}}},'' {\em Van
    Allen Probe Science Working Group -- RBSPICE Team Meeting}, March 11,
    2014.

\end{itemize*}


%%%% 2013
\begin{center} \Large{2013} \end{center}
\normalsize
\begin{itemize*}
  \item
    Urban, K., A. J. Gerrard, L. J. Lanzerotti, and D. G. Mitchell,
    ``\href{http://adsabs.harvard.edu/abs/2013AGUFMSM33A2129U}{Solar
    wind-driven ULF activity in Earth’s inner radiation belt:
    Effects on trapped electrons \textsuperscript{\tiny{[link]}}},'' {\em American Geophysical Union Fall
    Meeting}, San Francisco, CA. December 9-13, 2013.

  \item Urban, K., A. Gerrard, and L. Lanzerotti, ``Ground and
    spaceborne perspectives of ULF activity in Earth's radiation
    belts,'' {\em Geospace Environment Modeling [GEM] Summer Workshop},
    Snowmass, CO. June 16-21, 2013.

  \item
    Blackmore, D., A. Rosato, X. Tricoche, K. Urban, H. Wu, and L. Zou,
    ``Analysis of a dynamical systems model for granular flow,''  {\em SIAM
    Conf. on Applications of Dynamical Systems}, Snowbird Resort, Utah.
    May 18-23, 2013.


\end{itemize*}


%%%% 2012
\vspace{0.5cm}
\begin{center} \Large{2012} \end{center}
\normalsize
\begin{itemize*}
  \item Urban, K., and A. J. Gerrard,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:Se3iqnhoufwC}{Particle precipitation regimes of the polar
    cap in the midst of deep geomagnetic quiescence: perspectives from the
    AGO magnetometer network \textsuperscript{\tiny{[link]}}},'' {\em American Geophysical Union Fall
    Meeting}, San Francisco, December 3-7, 2012.

  \item Teti, A., A. Gerrard, J. Olsztyn, Y. Bhattacharya, G.
    Jeffer, K. Urban, L. Lanzerotti, and A. Weatherwax,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:UebtZRa9Y70C}{Ground
    Sites: Mapping of Solar Wind KHI Periodicities and the Subsequent
    Generation of Compressional/Breathing Pc5 Modes \textsuperscript{\tiny{[link]}}},''
    {\em American Geophysical Union Fall
    Meeting}, San Francisco, December 3-7, 2012.

  \item
    Nahm, A., S. Potter, KS Sayanagi, S. Diniega, S. Gil, J. Balcerski,
    B.  Carande, R. Diaz-Silva, A. Fraeman, J. Hudson, S. Guzewich, R.
    Livi, M.  Route, K. Urban, S. Vasisht, B. Williams, C. Budney, and L. Lowes,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:Tyk-4Ss8FVUC}{TASTER:
    Trojan ASteroid Tour, Exploration, and Rendezvous, a JPL Planetary
    Science Summer School Mission Design Exercise \textsuperscript{\tiny{[link]}}},'' {\em Lunar and
    Planetary Science Conference}. Vol. 43. 2012.
\end{itemize*}



%%%% 2011
\begin{center} \Large{2011} \end{center}
\normalsize
\begin{itemize*}

  \item Bhattacharya, Y., A. Gerrard, K. Urban, L. Lanzerotti, and A.
    Weatherwax, ``Spectral investigation of PC5 oscillations in SWEPAM proton
    velocities from the ACE spacecraft,'' {\em CEDAR-GEM Joint
    Workshop}, Santa Fe, NM. June 26 - July 1, 2011.

  \item Urban, K., A. Gerrard, L. Lanzerotti, Y. Bhattacharya, A. Ridley, and A.
    Weatherwax,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:Y0pCki6q_DkC}{Synoptic-scale magnetometer observations of the open-closed
    field line boundary \textsuperscript{\tiny{[link]}}},'' {\em American Geophysical Union Fall
    Meeting}, San Francisco, CA. December 5-9, 2011.

  \item
    Bhattacharya, Y., A. Gerrard, K. Urban, L. Lanzerotti, and D.
    Thomson,``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:YsMSGLbcyi4C}{Solar
    p-mode frequency plasma waves in high speed solar wind streams \textsuperscript{\tiny{[link]}}},''
    {\em American Geophysical Union Fall Meeting}, San Francisco,
    CA. December 5-9, 2011.

  \item
    R. Diaz-silva, K. Sayanagi, S. Gil, S. Diniega, J. Balcerski, B. Benneke,
    B. Carande, A. Fraeman, J. Hudson, S. Guzewich, R. Livi, A. Nahm, S.
    Potter, M. Route, K. Urban, S. Vasisht, B. Williams, C. Budney, and L.
    Lowes,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&citation_for_view=KTLuoQkAAAAJ:W7OEmFMy1HYC}{TASTER:
    Trojan ASteroid Tour, Exploration and Rendezvous, a NASA Planetary
    Science Summer School Mission Design Exercise \textsuperscript{\tiny{[link]}}},'' {\em American
    Geophysical Union Fall Meeting}, San Francisco, CA. December
    5-9, 2011.

  \item Urban, K., Y. Bhattacharya, A. Gerrard, L. Lanzerotti,
    ``\href{http://www.srl.caltech.edu/ACE/meetings/Nov.2011meeting/}{ULF
    periodicities in the solar wind: drivers of magnetospheric
    ULF \textsuperscript{\tiny{[link]}}},'' {\em ACE Science Team Meeting}, Applied Physics Laboratory, Johns Hopkins
    University, Laurel, MD. Nov 1-2, 2011.

  \item
    Bhattacharya, Y., K. Urban, A. Gerrard, L. Lanzerotti, A.
    Weatherwax, and K. Keika, ``Synoptic variation of the OCB during
    CIR-driven events: issues with the Pc5 periodicities in the solar
    wind?,'' {\em Japan Geoscience Union Meeting}, Chiba, Japan. May
    22-27, 2011.

  \item
    Bhattacharya, Y., K. Urban, A. Gerrard, L. Lanzerotti, and A.
    Weatherwax, ``Synoptic variation of the OCB during CIR-driven events:
    issues with the Pc5 periodicities in the solar wind?,'' {\em 
    PENGUIn-AGO Workshop}, Berkeley, CA. March 17-18, 2011.
    

  \item Urban, K., Bhattacharya, Y., A. Gerrard, L. Lanzerotti,
    ``Quiet-time observations of the open-closed boundary prior to the
    CIR-induced storm of August 9, 2008,'' {\em 2011 PENGUIn-AGO
    Workshop}, UC-Berkeley, Berkeley, CA. March 17-18, 2011.

\end{itemize*}


%%%% 2010
\begin{center} \Large{2010} \end{center}
\normalsize
\begin{itemize*}
  \item 
    Urban, K., A. J. Gerrard, A. Ridley, L. Lanzerotti, and A. Weatherwax,
    ``Synoptic Observations of Open-Closed Boundary Variations at Solar
    Minimum,'' {\em Autonomous Polar Observing Systems Workshop}, Potomac, MD,
    September 30-October 1, 2010.

  \item
    Blackmore, D., A. Rosato, K. Urban, and X. Tricoche, ``Tapping Dynamics
    of Granular Configurations: Theory and Applications,'' {\em Gordon
    Conference on Granular and Granular-Fluid Flow}, Colby College,
    Maine, June 20-25, 2010.


\end{itemize*}


%%%% 2008
\begin{center} \Large{2008} \end{center}
\normalsize
\begin{itemize*}
  \item 
    Urban, K., A.  Gerrard, N. Hauser, R. Melville, and L. Lanzerotti,
    ``\href{https://scholar.google.com/citations?view_op=view_citation&hl=en&user=KTLuoQkAAAAJ&sortby=pubdate&citation_for_view=KTLuoQkAAAAJ:2osOgNQ5qMEC}{The
    NJIT-UACNJ-PSU Collaborative: Magnetometer measurements from northwest
    New Jersey in collaboration with South Pole magnetometer measurements
    from the PENGUIn-AGO instrumentation \textsuperscript{\tiny{[link]}}},'' 
    {\em American Geophysical Union 2008 Fall Meeting}, 
    San Francisco, CA. December 2008.
\end{itemize*}


%%%% 2007
\begin{center} \Large{2007} \end{center}
\normalsize
\begin{itemize*}
  \item 
    Urban, K., and N. Phillips, ``The Absolute Spectrum Polarimeter: Is a rapid inflationary period
    a real possibility in the early universe?'',
    {\em NASA - Goddard Space Flight Center - Internship Presentations},
    Greenbelt, MD. August 2007.
\end{itemize*}

%%%% 2006
\begin{center} \Large{2006} \end{center}
\normalsize
\begin{itemize*}
  \item 
    Urban, K., and B. Thompson, 
    ``The Space Weather Survival Guide,''
    {\em NASA - Goddard Space Flight Center - Internship Presentations},
    Greenbelt, MD. August 2006.
\end{itemize*}

