\begin{itemize*}

  %\item
  %  % Urban, K. D., A. J. Gerrard, L. J. Lanzerotti, and A. T.  Weatherwax.
  %  Penetration of solar wind hydromagnetic
  %  energy deep into the polar cap: remote detection and forecasting. 
  %  Geophysical Research Letters,
  %  Submitted, 2016.

  %%%%%%%%%%%%%%%%%%% 2016 %%%%%%%%%%%%%%%%%%%%%%%%%
  \item \label{itm:sw-2016-eccentric}
    Urban, K. D., A. J. Gerrard, L. J. Lanzerotti, and A. T. Weatherwax.
    Rethinking the polar cap: Eccentric-dipole structuring of ULF power at the highest corrected geomagnetic latitudes.
    Journal of Geophysical Research, Space Physics, Vol. 121, 2016.

  \item \label{itm:sw-2016-phd} 
    Urban, Kevin.
    The hydromagnetic structure of the polar cap and its interaction
    with the solar wind.  PhD Dissertation. 
    New Jersey Institute of Technology \& Rutgers University, 
    Department of Physics, 2016.
    

  %%%%%%%%%%%%%%%%%%% 2014 %%%%%%%%%%%%%%%%%%%%%%%%%
  \item \label{itm:gran-2014-reduced}
    Blackmore, D., A. Rosato, X. Tricoche, K. D. Urban, and L. Zou,
    Analysis, simulation, and visualization of 1D tapping via reduced dynamical models.
    Physica D: Nonlinear Phenomena, Vol.  273, 2014.

  %%%%%%%%%%%%%%%%%%% 2013 %%%%%%%%%%%%%%%%%%%%%%%%%
  \item \label{psss-2013-trojan}
    Diniega, S., K. Sayanagi, J. Balcerski, B. Carande, R. Diaz-Silva,
    A. Fraeman, S. Guzewich, J. Hudson, A. Nahm, S. Potter, M. Route, K.
    D. Urban, S. Vasisht, B. Benneke, S. Gil, R. Livi, B. Williams, and C.
    Budney, L. Lowes.
    Mission to the Trojan Asteroids: Lessons learned during a JPL Planetary Science Summer School mission design exercise.
    Planetary and Space Science, Vol. 76, 2013.

  \item \label{itm:gran-2013-simulations}
    Rosato, A., D. Blackmore, X. M. Tricoche, K. D. Urban, and L. Zuo,
    Dynamical systems model and discrete element simulations of a tapped granular column.
    Powders and Grains 2013: Proceedings of the 7th International Conference 
    on Micromechanics of Granular Media. Vol. 1542. No. 1. AIP Publishing, 2013.

  %%%%%%%%%%%%%%%%%%% 2011 %%%%%%%%%%%%%%%%%%%%%%%%%
  \item \label{sw-2011-quiet-time}
    Urban, K. D., Y. Bhattacharya, A. J. Gerrard, A. Ridley, L. Lanzerotti,
    and A. Weatherwax.
    Quiet-time observations of the open-closed boundary prior to the CIR-induced storm of August 9, 2008.
    Space Weather, Vol. 9, S11001, 2011.

  \item \label{itm:gran-2011-tapping}
    Blackmore, D., A. Rosato, X. Tricoche, K. Urban, and V. Ratnaswamy.
    Tapping dynamics for a column of particles and beyond.
    Journal of Mechanics of Materials and Structures, Vol. 6, No. 1-4, 2011.

  %%%%%%%%%%%%%%%%%%% 2010 %%%%%%%%%%%%%%%%%%%%%%%%%
  \item \label{itm:gran-2010-fractional}
    Blackmore, D., K. Urban, and A. Rosato,
    Integrability analysis of regular and fractional Blackmore-Samulyak-Rosato fields.
    Condensed Matter Physics, Vol. 13, No. 4, 2010. 

  \item \label{itm:sw-2010-masters}
    Urban, Kevin.
    Synoptic Variability of a {CIR}-driven Open-{C}losed Boundary During Solar Minimum.
    Master's Thesis. New Jersey Institute of Technology \& Rutgers University,
    Department of Physics, 2010.

\end{itemize*}
